Price of Anarchy for Mean Field Games

### 2018-07-21 PoA.tex
prop 4 second half

\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}
	Moreover, if
		$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	then
	$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

@@

	For the sake of simplicity, let's denote $\displaystyle \kappa_u = \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1 - \bar{s})} } $ and $\zeta_1 = r + \bar{r}(1-\bar{s})^2$.
	We expand firstly $\lambda$, $C^u$, $D^u$ and $\delta^{\pm}_u$ in terms of $b_2$, namely
	\begin{equation*}
	\begin{array}{rclcrcl}
	\frac{b_2}{b_2 + \bar{b}_2} &=& 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) &\qquad& 
	\lambda &=& \frac{\zeta_1}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \\
	C^u &=& \zeta_1 \kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) &\qquad&
	D^u &=& \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) 
	\end{array}
	\end{equation*}
	and 
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^u}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&=& \frac{A^u}{b_2} \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) \pm \sqrt{\kappa_u^2 \left( 1 - \frac{\bar{b}_2}{b_2} + \mathcal{O}(b_2^{-2}) \right) + \mathcal{O}(b_2^{-2}) } \\
		&=& \pm \kappa_u + \left(A^u \mp \frac{\bar{b}_2}{2}\kappa_u \right) \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
	\end{IEEEeqnarray*}

	Thus, for $b_2$ tends to infinity, we have $$e^{-(\delta_u^+ - \delta_u^-) (T-t)} = e^{-( (2 b_2+\bar{b}_2)\kappa_u (T-t) + \mathcal{O}(b_2^{-1}) }$$
	which is uniformly bounded over $[0,T]$. Clearly, $e^{-(\delta_u^+ - \delta_u^-) (T-t)} = \mathcal{O}(b_2^{-2}) \to 0$ for $t \in [0, T)$.

	The next step is to give an estimation of $\Delta SC$. To do so, we need to expand the product $B u_t$ up till $b_2^{-2}$. We first notice that for $t \in [0,T)$, 
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u_t &=& \frac{ \displaystyle - \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^+_u}{b_2 + \bar{b}_2}\right) + \left(\frac{C^u}{b_2 + \bar{b}_2} + D^u \cdot \frac{\delta^-_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^+_u - \delta^-_u)(T-t)} }
		{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) - \left(\frac{\delta^+_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^+_u - \delta^-_u)(T-t)}  } \nonumber \\
		&=& \frac{ - (\mathcal{O}(b_2^{-1}) + \zeta_1 \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} \kappa_u + \mathcal{O}(b_2^{-1}) ) + \mathcal{O}(b_2^{-2})}{(\mathcal{O}(b_2^{-1})- \frac{q_T + \bar{q}_T(1-s)}{r + \bar{r}(1-\bar{s})} ) - \mathcal{O}(b_2^{-2}) } \nonumber \\
		&=& \zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})
	\end{IEEEeqnarray*}
	Then, we can continue do the expansion and obtain
	\begin{IEEEeqnarray*}{rCl}
		&&(b_2 + \bar{b}_2) ( (b_2 + \bar{b}_2) u_t - \zeta_1 \kappa_u ) \nonumber\\
		&=& \frac{-(C^u + D^u \delta^+_u) + \mathcal{O}(b_2^{-2}) }{\displaystyle \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{r + \bar{r}(1-\bar{s})^2} \right) + \mathcal{O}(b_2^{-2}) } - (b_2 + \bar{b}_2) \zeta_1 \kappa_u \nonumber \\
		&=& \frac{-\left( C^u + D^u \delta_u^+ + (b_2 + \bar{b}_2) \zeta_1 \kappa_u \left( \frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right) \right) + \mathcal{O}(b_2^{-2})}{  \left(\frac{\delta^-_u}{(b_2 + \bar{b}_2)^2} - \frac{D^u}{\zeta_1} \right)-  \mathcal{O}(b_2^{-2})} \nonumber \\
		&=& \frac{  -\left( C^u +\zeta_1 \kappa_u \frac{\delta_u^-}{b_2 + \bar{b}_2} +  D^u (b_2 + \bar{b}_2)(\frac{\delta^+_u}{b_2 + \bar{b}_2} - \kappa_u) \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1}) } \nonumber \\
		&=& \frac{- \left( \zeta_1 \kappa_u^2 (1 -\frac{\bar{b}_2}{b_2} )  + \zeta_1 \kappa_u (- \kappa_u + (A^u + \frac{\bar{b}_2}{2} \kappa_u) \frac{1}{b_2}) ) + D^u (b_2 + \bar{b}_2) \left[ (A^u - \frac{\bar{b}_2}{2} \kappa_u )\frac{1}{b_2} + \mathcal{O}(b_2^{-2}) \right] \right) + \mathcal{O}(b_2^{-2}) }{ - \frac{D^u}{\zeta_1} + \mathcal{O}(b_2^{-1})} \nonumber \\
		&=& \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u ) + \mathcal{O}(b_2^{-1})
	\end{IEEEeqnarray*}
	Thus, we have for any given $t \in [0,T)$,
	\begin{equation*}
		(b_2+\bar{b}_2)^2 u_t = \zeta_1 \kappa_u (b_2 + \bar{b}_2) + \zeta_1 (A^u - \frac{\bar{b}_2}{2} \kappa_u) + h_t(b_2)
	\end{equation*}
	where $h_t(b_2) = \mathcal{O}(b_2^{-1})$.
	Since for any $t \in [0,T)$, $\int_0^t h_s(b_2) ds = \mathcal{O}(b_2^{-1})$ and $B = (b_2+ \bar{b}_2)^2 / \zeta_1$, we deduce that 
	\begin{equation*}
	\bar{x}_t^{MFG} = \mathbb{E}(\xi) e^{\int_0^t (b_1 + \bar{b}_1 - B u_s) ds} = \mathbb{E}(\xi) e^{(b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t + \mathcal{O}(b_2^{-1}) }
	\end{equation*}
	which tends uniformly to $0$ over $[0,T)$ as $b_2 \to \infty$.
	Moreover, since 
	\begin{equation*}
	\begin{split}
		(b_2 + \bar{b}_2) (u_t - w_t) 
	= (\zeta_1 \kappa_u + \mathcal{O}(b_2^{-1})) - (\sqrt{\zeta_1 (q+\bar{q}(1-s)^2)} + \mathcal{O}(b_2^{-1}) )\\
	= \sqrt{\zeta_1} (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})
	\end{split}
	\end{equation*}
	Thus
	\begin{IEEEeqnarray*}{rCl}
		\Delta SC &=& \frac{1}{2} \frac{(b_2+\bar{b}_2)^2}{\zeta_1} \int_0^T (u_t - w_t)^2 (\bar{x}_t^{MFG})^2 dt \\
		&=& \frac{\mathbb{E}(\xi)^2}{2} \int_0^T \left[ (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) + \mathcal{O}(b_2^{-1})\right]^2 \cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} e^{-2 \int_0^t h_s(b_2) ds} dt\\
		&=& \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
		&& + \frac{\mathbb{E}(\xi)^2  (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt
	\end{IEEEeqnarray*}

	For the first term, a direct computation yields that
	\begin{equation*}
	\begin{array}{rl}
	&\frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \int_0^T e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t} dt \\
	&= \frac{ \mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{2} \frac{1}{2(b_1 + \bar{b}_1- (A^u - \bar{b}_2 \kappa_u /2) - \bar{b}_2 \kappa_u) - 2 \kappa_u b_2} \left(e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) T} -1 \right) \\
	&= \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2})
	\end{array}
	\end{equation*}
	For the second term, we know that 
	$$ \left\vert e^{-2\int_0^t h_s(b_2) ds} - 1 \right\vert \leq \left\vert e^{ \mathcal{O}(b_2^{-1}) } -1 \right\vert = \mathcal{O}(b_2^{-1}).$$
	Together with the estimation of the first term above, we have 
	$$ \int_0^T \left[ (1 + \mathcal{O}(b_2^{-1}) ) e^{-2 \int_0^t h_s(b_2)} -1\right]\cdot e^{2 (b_1+\bar{b}_1 - \kappa_u (b_2 + \bar{b}_2) - (A^u - \bar{b}_2 \kappa_u / 2) ) t}  dt = \mathcal{O}(b_2^{-2}).$$
	Hence, we deduce that
	\begin{equation}
		\Delta SC = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{b_2} + \mathcal{O}(b_2^{-2}).
	\end{equation}

	Similarly, we can have $SC^{MKV} =  \frac{\zeta_2}{b_2} + \mathcal{O}(b_2^{-2})$
	for some constant $\zeta_2 \neq 0$. Thus,
	\begin{equation}
		\frac{\Delta SC}{SC^{MKV}} = \frac{\mathbb{E}(\xi)^2 (\sqrt{\zeta_1 \kappa_u^2} - \sqrt{q+\bar{q}(1-s)^2}) ^2}{4 \kappa_u} \frac{1}{\zeta_2} + \mathcal{O}(b_2^{-1})
	\end{equation}
	Therefore, if $ \zeta_1 \kappa_u^2 \neq q + \bar{q}(1-s)^2$, i.e.
	$$\frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + \bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	we have
	$$ \lim_{b_2 \to \infty} PoA =: PoA^{\infty,b_2} > 1;$$
	otherwise $$ \lim_{b_2 \to \infty} PoA = 1.$$

>>>>

% proposition b_2
\begin{proposition}
	Assuming (\ref{eq:assumptions}), if initial condition $\xi$ satisfies $\mathbb{E}(\xi)\neq 0$, and if furthermore, $\bar{b}_2= 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	 \lim_{b_2 \to 0} PoA =: PoA^{0,b_2} > 1.
	\end{equation*}

	%Moreover, if
	%	$$ \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q + %\bar{q}(1-s)^2}{q + \bar{q}(1-s)},$$
	%then
	%$$\lim_{b_2 \to \infty} PoA =: PoA^{\infty, b_2} > 1,$$
	%otherwise
	$$ \lim_{b_2 \to \infty} PoA = 1.$$	
	\label{prop:b2}
\end{proposition}

@@

	% b_2 to infty

@@

	When $b_2 \to \infty$, we have 
	\begin{equation*}
	\begin{array}{l}
	\lambda^{b_2} \to \frac{r + \bar{r}(1-\bar{s})^2}{r + \bar{r}(1-\bar{s})} =: \lambda^{b_2 \to \infty}\\
	B^{b_2} \to \infty, \qquad B^{\eta,b_2} \to \infty\\
	C^{u,b_2} \to \lambda^{b_2 \to \infty} ( q + \bar{q}(1-s)) =: C^{u,b_2 \to \infty}, \qquad D^{u,b_2} \to \lambda^{b_2 \to \infty} (q_T + \bar{q}_T(1-s_T)) =: D^{u,b_2 \to \infty} \\
	A^{u}, A^{w}, C^w, D^w, A^{\eta}, C^{\eta}, D^{\eta} \text{ are independent of } b_2
	\end{array}
	\end{equation*}
	Moreover
	\begin{IEEEeqnarray*}{rCl}
		\frac{\delta_u^{\pm,b_2}}{b_2 + \bar{b}_2} &=& \frac{A^u}{b_2 + \bar{b}_2} \pm \sqrt{\frac{C^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} + \frac{(A^u)^2}{(b_2+\bar{b}_2)^2} }\\
		&\xrightarrow[b_2 \to \infty]{}& \displaystyle \pm \sqrt{\frac{q + \bar{q}(1-s)}{r + \bar{r}(1-\bar{s})} } =: \pm c_{\delta_u^{b_2 \to \infty}}
	\end{IEEEeqnarray*}
	Thus we have $\delta^{+,b_2}_u - \delta^{-,b_2}_u \xrightarrow[b_2 \to \infty]{} +\infty$ and for any $t \in [0,T)$,
	$$\displaystyle  e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} \xrightarrow[b_2 \to \infty]{} 0.$$
	From the explicit formula (\ref{eq:riccati_ut_sol}) of $u_t^{b_2}$, we can compute the limit of $(b_2 + \bar{b}_2) u_t^{b_2}$ for any $t \in [0,T)$ by dividing the numerator with $(b_2 + \bar{b}_2)$ and the denominator with $(b_2)+\bar{b}_2)^2$, namely
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) u^{b_2}_t &=& \frac{ \displaystyle  \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{+,b_2}_u}{b_2 + \bar{b}_2}\right) - \left(\frac{C^{u,b_2}}{b_2 + \bar{b}_2} + D^{u,b_2} \cdot \frac{\delta^{-,b_2}_u}{b_2 + \bar{b}_2}\right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)} }
		{\displaystyle \left(\frac{- \delta^{-,b_2}_u}{(b_2 + \bar{b}_2)^2} + \frac{D^{u,b_2}}{r + \bar{r}(1-\bar{s})^2} \right) + \left(\frac{\delta^{+,b_2}_u}{(b_2 + \bar{b}_2)^2} - \frac{D^{u,b_2} }{r + \bar{r}(1-\bar{s})^2} \right)e^{- (\delta^{+,b_2}_u - \delta^{-,b_2}_u)(T-t)}  } \nonumber \\
		&&\\
		&\xrightarrow[b_2 \to \infty]{}& \quad (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_u^{b_2 \to \infty}}  =: c_3
	\end{IEEEeqnarray*}
	Idem, we can have for any $t \in [0,T)$,
	$$ (b_2 + \bar{b}_2) w_t^{b_2} \xrightarrow[b_2 \to \infty]{}  (r + \bar{r}(1-\bar{s})^2) \cdot c_{\delta_w^{b_2 \to \infty}} =: c_4,\qquad \text{with } \quad c_{\delta_w^{b_2 \to \infty}} = \sqrt{ \frac{q + \bar{q}(1-s)^2}{r + \bar{r}(1-\bar{s})^2} };$$
	and for any $t \in [0,T)$,
	$$ b_2 \eta_t^{b_2} \xrightarrow[b_2 \to \infty]{} (r+ \bar{r}) c_{\delta_\eta^{b_2 \to \infty}} =: c_5, \qquad \text{with } \quad c_{\delta_\eta^{b_2 \to \infty}} = \sqrt{\frac{q+\bar{q}}{r + \bar{r}}}.
	$$

	The next step is to provide an estimation of the order of magnitude of $\Delta SC$ and $SC^{MKV}$. For all $t \in [0,T)$, we denote $h_u(b_2,t) = (b_2 + \bar{b}_2) u_{t}^{b_2}$, $h_w(b_2,t) = (b_2 + \bar{b}_2)w_t^{b_2}$ and $h_\eta(b_2,t) = b_2 \eta_t^{b_2}$.\\

	Since $u_t^{b_2}$, $w_t^{b_2}$ and $\bar{x}_t^{MFG,b_2}$ are continuous functions on $[0,T]$, we deduce that the functions $\displaystyle t \mapsto \int_0^t u_s^{b_2} ds$ and $\displaystyle t \mapsto \int_0^t (u_s^{b_2}- w_s^{b_2})^2 (\bar{x}_s^{MFG,b_2})^2 ds$ are continuous on $[0,T]$ and differentiable on $(0,T)$. Then with equation (\ref{eq:x_bar_MFG_explicit_new_notation}), we can apply the Mean Value Theorem so that there exists two fixed times $0 < t_2 < t_1 < T$ for which
	\begin{IEEEeqnarray}{rCl}
		\Delta SC &=& \frac{1}{2} B^{b_2} \int_0^T (u^{b_2}_t- w^{b_2}_t)^2 (\bar{x}_t^{MFG,b_2} )^2 dt  \nonumber \\
		&=& \frac{1}{2} B^{b_2}  (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 (\bar{x}_{t_1}^{MFG,b_2} )^2  \cdot T \nonumber \\
		&=& \frac{T  B^{b_2} }{2} \cdot (u_{t_1}^{b_2}- w_{t_1}^{b_2} )^2 \cdot \mathbb{E}[\xi]^2 \exp \left( 2 (b_1 + \bar{b}_1) t_1 - 2\int_0^{t_1} B^{b_2} u_s^{b_2} ds \right) \nonumber \\
		&=&  \kappa_1 \left[ (b_2 + \bar{b}_2) (u_{t_1}^{b_2}- w_{t_1}^{b_2} ) \right]^2\cdot  \exp \left( - 2 B^{b_2} u_{t_2}^{b_2} \cdot t_1 \right) \nonumber \\
		&= & \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)},
		\label{eq:delta_SC_b_2_infty}
	\end{IEEEeqnarray}
	where  $\displaystyle \kappa_1 =\frac{T \mathbb{E}[\xi]^2 e^{2 (b_1 + \bar{b}_1) t_1}}{2 (r + \bar{r}(1-\bar{s})^2)} >0$ and $\displaystyle \kappa_2 = \frac{2 t_1}{r + \bar{r}(1-\bar{s})^2} >0 $ are two positive constants independent of $b_2$.\\

	Similarly, with equation (\ref{eq:v_t_new_notation}) of the variance $v_t$, we know that the functions $t \mapsto v_t$ and $\displaystyle t \mapsto \int_0^t (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds $ are continuous on $[0,T]$ and differentiable on $(0,T)$. Then the Mean Value Theorem yields that there exists a time  $t_3 \in (0,T)$ so that 
	\begin{equation}
	 \int_0^T (q+ \bar{q} + B^{\eta,b_2} (\eta_s^{b_2})^2 ) v_s^{b_2} ds = \left(q + \bar{q} + \frac{1}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} \cdot T,
	\label{eq:vt_int_b_2_infinity}
	\end{equation}
	and	there exists 3 time points $t_4, t_5, t_6$ satisfying $0<t_4 < T$ and $0 < t_5 < t_6 < T$ so that
	\begin{IEEEeqnarray}{rCl}
		v^{b_2}_T &=& Var(\xi) \exp \left( 2 \int_0^T (b_1 - B^{\eta,b_2} \eta_s^{b_2}) ds \right) + \sigma^2 \int_0^T \exp \left(2 \int_s^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right)	ds \nonumber \\
		&=& Var(\xi) e^{2b_1 T} \exp \left(-2 B^{\eta,b_2} \eta_{t_4}^{b_2} \cdot T \right) + \sigma^2 \exp\left(2 \int_{t_5}^T (b_1 - B^{\eta,b_2} \eta_u^{b_2}) du \right) \cdot T \nonumber \\
		&=&  Var(\xi) e^{2b_1 T} e^{-\frac{2T}{r+\bar{r}} b_2 h_\eta(b_2,t_4)} + \sigma^2 T e^{2b_1 (T-t_5)} \exp \left( -2 B^{\eta,b_2} \eta_{t_6}^{b_2} (T-t_5) \right) \nonumber \\
		&=& \kappa_3 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)}
	\label{eq:vt_b_2_infinity} 
	\end{IEEEeqnarray}
	where
	$\displaystyle \kappa_3 = Var(\xi) e^{2b_1 T}, \  \kappa_4 = \frac{2T}{r+\bar{r}},\  \kappa_5 = \sigma^2 T e^{2b_1(T-t_5)}, \   \kappa_6 = \frac{2(T-t_5)}{r+ \bar{r}}$ are four positive constants independent of $b_2$.

	\begin{comment}
	Idem, there exists 3 time points $t_7,t_8,t_9$ with $0<t_7<t_3<T$ and $0<t_8<t_9<t_3<T$ such that
	\begin{equation}
		v^{b_2}_{t_3} = \kappa_8 e^{-\kappa_7 b_2 h_\eta(b_2,t_7)} + \kappa_{10} e^{-\kappa_9 b_2 h_\eta(b_2,t_9)}
	\label{eq:v_{t_3}_b_2_expansion}
	\end{equation}
	where $ \displaystyle \kappa_7 = \frac{2t_3}{r+ \bar{r}}, \  \kappa_8 =Var(\xi) e^{2b_1 t_3}, \  \kappa_9 = \frac{2 (t_3 - t_8)}{r+ \bar{r}}, \  \kappa_{10}= \sigma^2 t_3 e^{2b_1 (t_3 - t_8)}$.
	\end{comment}

	With equation (\ref{eq:delta_SC_b_2_infty}) and (\ref{eq:vt_int_b_2_infinity}), we can multiply $\Delta SC$ and $SC^{MKV}$ by $(b_2 +\bar{b}_2)$ and then deduce that
	\begin{IEEEeqnarray}{rCl}
		\frac{\Delta SC}{SC^{MKV}} &=& \frac{\displaystyle \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 \cdot  e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)} }{\displaystyle \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) v_{t_3}^{b_2} + (q_T + \bar{q}_T) v_T^{b_2} + \frac{1}{b_2+\bar{b}_2} (\mathbb{E}(\xi) )^2 h_w(b_2,0)  } \nonumber \\
		&=& \frac{l_{u,v}(b_2) \cdot (b_2 + \bar{b}_2) e^{- \kappa_2 (b_2 + \bar{b}_2) h_u(b_2,t_2)}} { l_\eta(b_2) \cdot b_2 v_{t_3}^{b_2}  + l_1(b_2) \cdot b_2 v_T^{b_2} + (\mathbb{E}(\xi))^2 h_w(b_2,0) }
	\label{eq:delta_SC_SC^MKV_b_2_infinity}
	\end{IEEEeqnarray}
	where 
	$\displaystyle l_{u,v}(b_2) = \kappa_1 \left[ h_u(b_2,t_1) - h_w(b_2,t_1) \right]^2 , \  l_\eta(b_2) =  \left( (q + \bar{q})T + \frac{T}{r + \bar{r}} h_\eta(b_2,t_3)^2 \right) \frac{b_2 + \bar{b}_2}{b_2}$
	and $\displaystyle l_1(b_2) = (q_T + \bar{q}_T) \frac{b_2 + \bar{b}_2}{b_2}$.	
	With the limits of $h_u(b_2,t), h_w(b_2,t)$ and $h_\eta(b_2,t)$ for any fixed $t \in [0,T)$, it is easy to check that 
	$$ l_{u,v}(b_2,t_3) \xrightarrow[b_2 \to \infty]{} \kappa_1 (c_3 - c_4)^2, \quad l_\eta(b_2) \xrightarrow[b_2 \to \infty]{} (q+ \bar{q} + \frac{c_5^2}{r+ \bar{r}})T,\quad l_1(b_2) \xrightarrow[b_2 \to \infty]{} q_T + \bar{q}_T.$$

	Finally, we will show that for any fixed $t \in [0,T)$ and $\kappa >0$, we have
	\begin{equation}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2 \to \infty]{} 0 \qquad \text{and} \qquad b_2 e^{-\kappa b_2 h_\eta(b_2, t)} \xrightarrow[b_2 \to \infty]{} 0.
	\label{eq:b_2_vt_limit}
	\end{equation}
	Therefore, the numerator of equation (\ref{eq:delta_SC_SC^MKV_b_2_infinity}) tends towards $0$ whilst the denominator tends towards $(\mathbb{E}(\xi))^2 c_4>0$ because equation (\ref{eq:vt_b_2_infinity}) gives raise to
	$$ b_2 v_T^{b_2} = \kappa_3 \cdot b_2 e^{-\kappa_4 b_2 h_\eta(b_2,t_4)} + \kappa_5 \cdot b_2 e^{-\kappa_6 b_2 h_\eta(b_2,t_6)} \xrightarrow[b_2 \to \infty]{} 0,$$
	and so $b_2 v_{t_3}^{b_2} \xrightarrow[b_2 \to \infty]{} 0$.
	Together with the limits of $l_{u,v}(b_2), l_\eta(b_2)$ and $l_1(b_2)$, we have
	$$ \frac{\Delta SC}{SC^{MKV}} \xrightarrow[b_2 \to \infty]{} 0.$$

	Take $(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)}$ as an example. For any $t \in [0,T)$, we previously showed that $\lim_{b_2 \to \infty} h(b_2,t) = c_3 >0$. Let $\epsilon_1 >0$ such that $c_3 - 2 \epsilon_1 >0$. Then there exists $b_2^* > 0$ so that for all $b_2 \geq b_2^{*}$ we have $\vert h_u(b_2,t) - c_3 \vert \leq \epsilon_1$. Thus $h_u(b_2,t) - c_2 + 2 \epsilon_1 > \epsilon_1$ and 
	\begin{IEEEeqnarray*}{rCl}
		(b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2, t)} &=& e^{- \kappa (b_2 + \bar{b}_2) (h_u(b_2,t) - c_3 + 2\epsilon_1)} \cdot e^{- \kappa (c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) } \\
		&\leq & e^{- \kappa (b_2^* + \bar{b}_2) \epsilon_1} \cdot \exp \left( - \kappa(c_3 - 2 \epsilon_1) (b_2 + \bar{b}_2) + \ln(b_2 + \bar{b}_2) \right).
	\end{IEEEeqnarray*}
	Since the first term in the right hand side of the above inequality is a constant depending only on $\epsilon_1$, and the second term tends towards $0$ when $b_2 \to \infty$, then we must have
	$$ (b_2 + \bar{b}_2) e^{-\kappa (b_2 + \bar{b}_2) h_u(b_2,t)} \xrightarrow[b_2\to \infty]{} 0, \quad \forall\   0 \leq t < T. $$
	Thus, the limits in (\ref{eq:b_2_vt_limit}) hold true and following the previous analysis we conclude that 
	$$ \lim_{b_2 \to \infty} PoA = 1.$$
\end{proof}
